---
title: "data_wrangling"
author: "Xiao Shi"
date: "September 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

please don't use read.csv
Really load the package that you'll use a lot, otherwise use it like janitor::
```{r data import}
litters_data = read_csv(file = "./data/FAS_litters.csv")
litters_data = janitor::clean_names(litters_data)
```

learning assignment: if the project is moved, absolute won't work, relative will work!
ciiiii is for pre-determined data types
```{r}
sas_pup = read_csv(file = "./data/FAS_pups.csv", col_types = 'ciiiii')
sas_pup = read_csv(file = "/Users/apple/Desktop/data_wrangling/data/FAS_pups.csv")
sas_pup = janitor::clean_names(sas_pup)

```

## Look at data

Look at litters data, skim is actually better than simply litters_data
```{r}
skimr::skim(litters_data)
```

Read excel data, you can specify the range to make the import more accurate
```{r}
library(readxl)
mlb11_data = read_excel("./data/mlb11.xlsx", n_max = 20)
head(mlb11_data, 5)
```
read_csv output as tibble, and recognize variables by the capital letter
read.csv output as base r data frame